---
title: "211027 Create missing values in complete dataset"
author: "Anne Margit"
date: "10/27/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(lcmm)
library(dplyr)
library(survival)
library(parallel)
library(mice)
library(tidyr)
library(skimr)
```

```{r}
load("dl.Rdata")
```


```{r}
dl$id <- as.numeric(dl$id)
dl$days <- as.numeric(dl$days)

dl <- as.data.frame(dl)
```

Select participants with >20 measurements (= baseline + 19) 
```{r}
dl$id <- as.factor(dl$id)
dl2 <- dl %>%
  group_by(id) %>%
  add_tally(wt = !is.na(Date))

dl_mini <- dl2 %>%
  filter(n > 20)
dl_mini$id <- as.numeric(dl_mini$id)
dl_mini$days <- as.numeric(dl_mini$days)
dl_mini <- as.data.frame(dl_mini)
```


Recode NAs into zeros for employment, coronaclose, leavehousewhy
Fill in missing living situation values (backwards; assuming living situation is somewhat stable), and recode NAs into zeros

Delete physical health (measured too infrequently), countryCitizen, Citizen, Neuro1-3 (we have sum score)
Fill in missing mental health values (from wave 1 to baseline)
Fill in happiness values (up)
Fill in PFS values (up)
Fill in neuroticism (sumscore) values (up)

Replace NAs in friend_online and other_online with 0


```{r}
dl_mini <- dl_mini %>%
  mutate_at(vars(Emp1:Emp14, CoronaClose1:CoronaClose6, HouseLeaveWhy1:HouseLeaveWhy8),
            ~replace(., is.na(.), 0))

dl_mini <- dl_mini %>%
  group_by(id) %>%
  fill(liv_sit:liv_other, .direction = "up")

dl_mini <- dl_mini %>%
  mutate_at(vars(liv_sit:liv_other), ~replace(., is.na(.), 0))

dl_mini <- dl_mini %>%
  select(-c(phys_health, countryCitizen, Citizen, Neuro1, Neuro2, Neuro3))

dl_mini <- dl_mini %>%
  group_by(id) %>%
  fill(ment_health, .direction = "up")

dl_mini <- dl_mini %>%
  group_by(id) %>%
  fill(happy, .direction = "up")

dl_mini <- dl_mini %>%
  group_by(id) %>%
  fill(PFS, .direction = "up") %>%
  ungroup()

dl_mini <- dl_mini %>%
  group_by(id) %>%
  fill(neuroticism, .direction = "up") %>%
  ungroup()

dl_mini <- dl_mini %>%
  mutate_at(vars(friend_online, other_online), ~replace(., is.na(.), 0))

skim(dl_mini)

```


Save as dl_mini_complete
```{r}
dl_mini_complete <- dl_mini

save(dl_mini_complete, file="dl_mini_complete")
```


Create random missings in happy
```{r}
result <- dl_mini %>%
  ampute(prop= 0.3)

mypatterns <- result$patterns

mypatterns[37] <- 0
mypatterns[1:36] <- 1
mypatterns[38:59] <- 1

result <- dl_mini %>%
  ampute(prop= 0.3, patterns = mypatterns)

dl_mini_miss_happy <- result$amp
```


Create missings in other variables too, except ID, Date, stringency, confirmedcases, confirmeddeaths, days, n 
```{r}
result <- dl_mini %>%
  ampute(prop= 0.3)

mypatterns <- result$patterns
  
mypatterns[2:6] <- 0
mypatterns[8:50] <- 0
mypatterns[54:57] <- 0

mypatterns[1] <- 1
mypatterns[7] <- 1
mypatterns[51:53] <- 1
mypatterns[58:59] <- 1

result <- dl_mini %>%
  ampute(prop= 0.3, patterns = mypatterns)

dl_mini_miss_all <- result$amp

skim(dl_mini_miss_all)

```

Save data
```{r}
save(dl_mini_miss_happy, file="dl_mini_miss_happy.Rdata")
save(dl_mini_miss_all, file="dl_mini_miss_all.Rdata")
```
